Bootstrapping Multi-atlas Hippocampal Segmentation with \mb

### 2013-05-30 paper.Rnw
bland-altman for ADNI-XVAL

bland_altman_plot <- function(x, y) {
  data = data.frame(x=x,y=y,diff=x-y)
  return(ggplot(data, aes(x= x, y = diff)) + 
    geom_hline(yintercept = mean(data$diff) + c(-2, 0, 2) * sd(data$diff), 
               linetype=2, color='brown') + 
    geom_point())
}

@@

@@

ggplot(melted, aes(x= SNT, y = diff)) + 
  facet_grid( DX ~ . ) + 
  geom_hline(yintercept = limits, linetype=2, color='brown') + 
  annotate("text", y = limits, x=Inf, label=round(limits,1), 
            hjust=1.1,vjust=-0.8, size=3) + 
  geom_point() + 
  xlab('Mean of manual and MAGeT-Brain hippocampal volume') + 
  ylab('Difference between Manual and MAGeT-Brain hippocampal volume') + 
  geom_smooth(method="lm", formula = y~x)
@
  \caption{Bland-Altman plot comparing manual (SNT) and \mb hippocampal volumes 
  in the \adnidataset dataset.}
  \label{fig:ADNI-scr-Bland-Altman}
\end{figure}

>>>>

bland_altman_plot <- function(x, y, c) {
  data = data.frame(x=x,y=y,diff=x-y, c=c)
  return(ggplot(data, aes(x= x, y = diff, colour = as.factor(c))) + 
    geom_hline(yintercept = mean(data$diff) + c(-2, 0, 2) * sd(data$diff), 
               linetype=2, color='brown') + geom_point())
}

@@

\begin{figure}
<<ADN1-bland-altman, cache=TRUE, dependson='ADNI1-Xval-prep'>>=
snt.unilateral.vols = read.csv('data/a2a_snt_volumes.csv')
a2a.best = subset(all_data, atlases == 9 &
                    templates.mb == 19 &
                    reg_method=='ANTS' &
                    method.mb =='Majority Vote')
a2a.best = merge(a2a.best, snt.unilateral.vols)
bland_altman_plot(a2a.best$volume.snt, a2a.best$volume.ma, a2a.best$DX) + geom_smooth(method="lm")
@
\end{figure}

@@

ggplot(melted, aes(x= SNT, y = diff, colour=DX)) + 
  geom_hline(yintercept = limits, linetype=2, color='brown') + 
  annotate("text", y = limits, x=Inf, label=round(limits,1), 
            hjust=1.1,vjust=-0.8, size=3) + 
  geom_point() +  
  xlab('Mean of manual and MAGeT-Brain hippocampal volume') + 
  ylab('Difference between Manual and MAGeT-Brain hippocampal volume') + 
  geom_smooth(method="lm", formula = y~x)
@
  \caption{Bland-Altman plot comparing manual (SNT) and \mb hippocampal volumes 
  in the \adnidataset dataset.}
  \label{fig:ADNI-scr-Bland-Altman}
\end{figure}
